Supplementary Materials on Bayesian Generalized Additive Models used to Analyse Temporal Trends in Job Ads

### 2025-05-17 analysis/paper/supplement-GAMS-details.qmd
update readme

    ggplot(smooth_data, 
           aes(x = year, 
               y = response_est)) +
            geom_point(data = raw_data %>% 
                         mutate(colour_hex = case_when(
                           becoming_more_scientific == "TRUE" ~ "#1b9e77",
                           .default = "#d95f02"
                         )),
                 aes(x = year,
                     y = value,
                     colour = colour_hex),
                 alpha = 0.7) +
      scale_color_identity() +
      # Add the line 
      geom_line(color = "#7570b3", 
                linewidth = 2) +
      geom_text(data = raw_data  %>% 
                  mutate(`Bayes R2` = r_sq) %>% 
                  mutate(max_value = max(value)) %>% 
                  distinct(`Bayes R2`, 
                           max_value),
           aes(
           x = 1980, 
           y = max_value, 
           label = paste("Pseudo R² = ", 
                         signif(`Bayes R2`, 
                                digits = 3))),
           hjust = 0, 
           vjust = 1.5,
           size = 2) +
    theme_bw(base_size = 6) +
      labs( 
           y = response_label, 
           x = "")
}

@@

plot_grid(plotlist = conditional_smooths_plots_list, ncol = 3)

>>>>

    ggplot(smooth_data, 
           aes(x = year, 
               y = response_est)) +
            geom_point(data = raw_data %>% 
                         mutate(colour_hex = case_when(
                           becoming_more_scientific == "TRUE" ~ "#1b9e77",
                           .default = "#d95f02"
                         )),
                 aes(x = year,
                     y = value,
                     colour = colour_hex),
                 alpha = 0.7) +
      scale_color_identity() +
      # Add the line 
      geom_line(color = "#7570b3", 
                linewidth = 2) +
      geom_text(data = raw_data  %>% 
                  mutate(`Bayes R2` = r_sq) %>% 
                  mutate(max_value = max(value)) %>% 
                  distinct(`Bayes R2`, 
                           max_value),
           aes(
           x = 1980, 
           y = max_value, 
           label = paste("Pseudo R² = ", 
                         signif(`Bayes R2`, 
                                digits = 3))),
           hjust = 0, 
           vjust = 1.5,
           size = 2) +
    theme_bw(base_size = 4) +
      labs( 
           y = response_label, 
           x = "")
}

@@

plot_grid(plotlist = conditional_smooths_plots_list, 
          ncol = 3,
          align = "hv",
          axis ="tblr")

ggsave(here::here("analysis/figures/fig-smooth-plots-paper.png"),
      dpi = 1000,
      bg = "white",
      h = 3,
      w = 5)
